### 2020-07-23 Research_[2020-05-18]_Piecewise_Monotone_Quintic_Fortran/paper/mqsi20.tex
Made modifications including Dr. Watsons recent revisions. Working towards a submission version.

\hrule\bigskip\smallskip \footnote{}{\hskip
-\parindent{\parindent=0pt\rmVIII Authors' addresses:
T. C. H. Lux, L. T. Watson, Departments of Computer Science, Mathematics,
and Aerospace and Ocean Engineering, Virginia Polytechnic Institute \&
State University, Blacksburg, VA 24061; e-mails: {\ttVIII tchlux@vt.edu,
ltwatson@computer.org}; T. H. Chang, Mathematics and Computer Science
Division, Argonne National Laboratory, 9700 South Cass Avenue, Bldg. 240,
Lemont, IL 60439; e-mail: {\ttVIII thchang@vt.edu}; W. I. Thacker, Winthrop
University, Rock Hill, SC 47405; {\ttVIII thackerw@winthrop.edu}.

@@

\medskip
Additional Key Words and Phrases: Quintic Spline, interpolation

@@

% ====================================================================
% Bibliography
\heading{\hlvVIII BIBLIOGRAPHY} {
\baselineskip=2pt \parskip=100mm
\frenchspacing
% Temporary 'caps', 'sl', and 'rm'.
\let\caps=\capsVIII
\let\sl=\slVIII
\let\rm=\rmeight \rmVIII

@@

%\refj is for regular journal articles
%  #1 -- Author(s)
%  #2 -- Year
%  #3 -- Title
%  #4 -- Journal
%  #5 -- Volume, number, and pages
\def\refj#1#2#3#4#5{\noindent\hangindent=10pt\hangafter=1
{\caps #1}\ys #2.\ys {\rm #3}. {\sl #4}, #5.\vskip 6pt}

%\refb is for books
%  #1 -- Author(s)
%  #2 -- Year
%  #3 -- Title
%  #4 -- Publisher, City, State
\def\refb#1#2#3#4{\noindent\hangindent=10pt\hangafter=1
{\caps #1}\ys #2.\ys{\sl #3}. {\rm #4}.\vskip 6pt}

%\reft is for tech. reports, theses, and conferences
%  #1 -- Author(s)
%  #2 -- Year
%  #3 -- Title
%  #4 -- Technical report ID, Publisher, City, State
\def\reft#1#2#3#4{\noindent\hangindent=10pt\hangafter=1
{\caps #1}\ys #2.\ys{\rm #3}. {\rm #4}.\vskip 6pt}

@@

% brennan2019measure
\refj{Brennan, A.}{2020}{Measure, Modulation and Metadesign: NC
  Fabrication in Industrial Design and Architecture}{Journal of Design
  History}{33(1):66--82}

@@

% cameron2019moana
\refj{Cameron, K. W., Anwar, A., Cheng, Y., Xu, L., Li, B., Ananth, U., Bernard, J., Jearls, C., Lux,  T. C. H., Hong, Y., Watson, L. T., and Butt, A. R.}{2019}{MOANA: Modeling and Analyzing I/O Variability in Parallel System Experimental Design}{IEEE Transactions on Parallel and Distributed Systems}{30(8):1843--1856}

@@

% hess1994positive
\refj{He{\ss}, W. and Schmidt, J. W.}{1994}{Positive quartic, monotone
  quintic $C^2$-spline interpolation in one and two dimensions}{Journal
  of Computational and Applied Mathematics}{55(1):51–-67}

@@

% yao2018unconditionally
\refj{Yao, J. and Nelson, K. E.}{2018}{An Unconditionally Monotone
  $C^2$ Quartic Spline Method with Nonoscillation
  Derivatives}{Advances in Pure Mathematics}{8(LLNL-JRNL-742107)}

>>>>

\hrule\bigskip\smallskip \footnote{}{\hskip
-\parindent{\parindent=0pt\rmVIII
This work was supported by National Science Foundation Grants CNS-1565314,
CNS-1838271, and DGE-154362.
Authors' addresses:
T. C. H. Lux, L. T. Watson, Departments of Computer Science, Mathematics,
and Aerospace and Ocean Engineering, Virginia Polytechnic Institute \&
State University, Blacksburg, VA 24061; e-mails: {\ttVIII tchlux@vt.edu,
ltwatson@computer.org}; T. H. Chang, Mathematics and Computer Science
Division, Argonne National Laboratory, 9700 South Cass Avenue, Bldg. 240,
Lemont, IL 60439; e-mail: {\ttVIII thchang@vt.edu}; W. I. Thacker, Winthrop
University, Rock Hill, SC 47405; {\ttVIII thackerw@winthrop.edu}.

@@

\medskip
Additional Key Words and Phrases: quintic spline, interpolation

@@

% ====================================================================
%                            Bibliography
% \vfil\goodbreak
\heading{\hlvVIII BIBLIOGRAPHY} {
\baselineskip=2pt%\parskip=100mm
\frenchspacing
% Temporary 'caps', 'sl', and 'rm'.
\let\caps=\capsVIII
\let\sl=\slVIII
\let\rm=\rmeight \rmVIII

@@

%\refj is for regular journal articles
%  #1 -- Author(s)
%  #2 -- Year
%  #3 -- Title
%  #4 -- Journal
%  #5 -- Volume, number, and pages
\def\refj#1#2#3#4#5{\noindent\hangindent=10pt\hangafter=1
{\caps #1}\ys #2.\ys {\rm #3}. {\sl #4}, #5.\vskip 6pt minus 3pt}

%\refb is for books
%  #1 -- Author(s)
%  #2 -- Year
%  #3 -- Title
%  #4 -- Publisher, City, State
\def\refb#1#2#3#4{\noindent\hangindent=10pt\hangafter=1
{\caps #1}\ys #2.\ys{\sl #3}. {\rm #4}.\vskip 6pt minus 3pt}

%\reft is for tech. reports, theses, and conferences
%  #1 -- Author(s)
%  #2 -- Year
%  #3 -- Title
%  #4 -- Technical report ID, Publisher, City, State
\def\reft#1#2#3#4{\noindent\hangindent=10pt\hangafter=1
{\caps #1}\ys #2.\ys{\rm #3}. {\rm #4}.\vskip 6pt minus 3pt}

@@

% brennan2019measure
\refj{Brennan, A.}{2020}{Measure, modulation and metadesign: NC
  fabrication in industrial design and architecture}{Journal of Design
  History}{33(1):66--82}

@@

% cameron2019moana
\refj{Cameron, K. W., Anwar, A., Cheng, Y., Xu, L., Li, B., Ananth, U.,
Bernard, J., Jearls, C., Lux,  T. C. H., Hong, Y., Watson, L. T., and Butt,
A. R.}{2019}{MOANA: modeling and analyzing I/O variability in parallel
system experimental design}{IEEE Transactions on Parallel and Distributed
Systems}{30(8):1843--1856}

@@

% hess1994positive
\refj{He{\ss}, W. and Schmidt, J. W.}{1994}{Positive quartic, monotone
  quintic $\scriptstyle C^2$-spline interpolation in one and two
  dimensions}{Journal of Computational and Applied Mathematics}{55(1):51–-67}

@@

% yao2018unconditionally
\refj{Yao, J. and Nelson, K. E.}{2018}{An unconditionally monotone
  $\scriptstyle C^2$ quartic spline method with nonoscillation
  derivatives}{Advances in Pure Mathematics}{8(LLNL-JRNL-742107)}
